---
title: "Week 11 Report"
author: "Jackson Tucker & Dylan Denner"
date: "4/6/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Exercises
8. We will now perform cross-validation on a simulated data set.
(a) Generate a simulated data set as follows:

set.seed(1)
x=rnorm(100)
y=x-2*x^2+rnorm (100)

In this data set, what is n and what is p? Write out the model
used to generate the data in equation form.


```{r}
library(boot)
setwd("C:/Users/dylan/Documents/R/MATH5530/Week11")

set.seed(1)
x <- rnorm(100)
y <- x -2*x^2 + rnorm(100)

df <- data.frame(x,y)
```

Here, n = 100, p = 2

(b) Create a scatterplot of X against Y . Comment on what you find.

```{r}
plot(x,y)

```

There is a very clear nonlinear, quadratic relationship between x and y. 


(c) Set a random seed, and then compute the LOOCV errors that
result from fitting the following four models using least squares:
i.    Y = β0 + β1X + e
ii.   Y = β0 + β1X + β2X2 + e
iii.  Y = β0 + β1X + β2X2 + β3X3 + e
iv.   Y = β0 + β1X + β2X2 + β3X3 + β4X4 + e

```{r}
set.seed(100)

model1 <- glm(y~x, data = df)
LOOCVerror1 <- cv.glm(df,model1)$delta
LOOCVerror1
```

```{r}
model2 <- glm(y~poly(x,2), data = df)
LOOCVerror2 <- cv.glm(df,model2)$delta
LOOCVerror2
```

```{r}
model3 <- glm(y~poly(x,3), data = df)
LOOCVerror3 <- cv.glm(df,model3)$delta
LOOCVerror3
```

```{r}
model4 <- glm(y~poly(x,4), data = df)
LOOCVerror4 <- cv.glm(df,model4)$delta
LOOCVerror4
```


(d) Repeat (c) using another random seed, and report your results.
Are your results the same as what you got in (c)? Why?

```{r}
set.seed(200)
x <- rnorm(100)
y <- x -2*x^2 + rnorm(100)

df <- data.frame(x,y)

model1_2 <- glm(y~x, data = df)
LOOCVerror1_2 <- cv.glm(df,model1_2)$delta
LOOCVerror1_2
```

```{r}
model2_2 <- glm(y~poly(x,2), data = df)
LOOCVerror2_2 <- cv.glm(df,model2_2)$delta
LOOCVerror2_2
```

```{r}
model3_2 <- glm(y~poly(x,3), data = df)
LOOCVerror3_2 <- cv.glm(df,model3_2)$delta
LOOCVerror3_2
```

```{r}
model4_2 <- glm(y~poly(x,4), data = df)
LOOCVerror4_2 <- cv.glm(df,model4_2)$delta
LOOCVerror4_2
```

(e) Which of the models in (c) had the smallest LOOCV error? Is
this what you expected? Explain your answer.



(f) Comment on the statistical significance of the coefficient estimates that results from fitting each of the models in (c) using
least squares. Do these results agree with the conclusions drawn
based on the cross-validation results?

```{r}
summary(model1)
```

```{r}
summary(model2)
```

```{r}
summary(model3)
```

```{r}
summary(model4)
```



## Preperation for Presentation


```{r, echo=FALSE}
setwd("C:/Users/dylan/Documents/R/MATH5530/Project/MATH5530/SCRIPTS/")
library(dplyr)
library(tidycensus)
library(tidyverse)
library(tidyr)
library(readxl)
library(readr)
library(gridExtra)
library(ggpubr)
library(MASS)
library(car)
library(lmtest)
library(dplyr)
library(tidycensus)
library(tidyverse)
library(tidyr)
library(readxl)

```



```{r}
library(tidycensus)

poverty_by_sex_edu_attainment <- get_acs(
  geography = "school district (unified)", 
  variables = c(total_population = "B17003_001",
                below_poverty_num = "B17003_002",
                below_poverty_num_men = "B17003_003",
                M_below_poverty_less_than_HS = "B17003_004",
                M_below_poverty_HS = "B17003_005",
                M_below_poverty_some_college = "B17003_006",
                M_below_poverty_bachelor_plus = "B17003_007",
                below_poverty_num_women = "B17003_008",
                W_below_poverty_less_than_HS = "B17003_009",
                W_below_poverty_HS = "B17003_010",
                W_below_poverty_some_college = "B17003_011",
                W_below_poverty_bachelor_plus = "B17003_012",
                above_poverty_num = "B17003_013",
                above_poverty_num_men = "B17003_014",
                M_above_poverty_less_than_HS = "B17003_015",
                M_above_poverty_HS = "B17003_016",
                M_above_poverty_some_college = "B17003_017",
                M_above_poverty_bachelor_plus = "B17003_018",
                above_poverty_num_women = "B17003_019",
                W_above_poverty_less_than_HS = "B17003_020",
                W_above_poverty_HS = "B17003_021",
                W_above_poverty_some_college = "B17003_022",
                W_above_poverty_bachelor_plus = "B17003_023"),
  state = "OH", 
  year = 2019)
```
```{r}
head(poverty_by_sex_edu_attainment)
dim(poverty_by_sex_edu_attainment)
length(unique(poverty_by_sex_edu_attainment$NAME))
```


```{r}

poverty_by_sex_edu_attainment <- poverty_by_sex_edu_attainment[,-c(5)]

```

```{r}
poverty_by_sex_edu_attainment <- spread(poverty_by_sex_edu_attainment, variable, estimate)

head(poverty_by_sex_edu_attainment)
dim(poverty_by_sex_edu_attainment)


```

```{r}
mod_poverty_by_sex_edu_attainment <- poverty_by_sex_edu_attainment %>% mutate(
  "tot_less_than_HS" = W_below_poverty_less_than_HS + M_below_poverty_less_than_HS + 
                      W_above_poverty_less_than_HS + M_above_poverty_less_than_HS,
  "tot_HS" = W_below_poverty_HS + M_below_poverty_HS + 
            W_above_poverty_HS + M_above_poverty_HS,
  "tot_some_college" = W_below_poverty_some_college + M_below_poverty_some_college + 
                    W_above_poverty_some_college + M_above_poverty_some_college,
  "tot_bachelor_plus" = W_below_poverty_bachelor_plus + M_below_poverty_bachelor_plus + 
                      W_above_poverty_bachelor_plus + M_above_poverty_bachelor_plus,
  "tot_HS_PLUS" = tot_HS + tot_some_college + tot_bachelor_plus,
  "poverty_percentage" = below_poverty_num/total_population,
  "HS_PLUS_percentage" = tot_HS_PLUS/total_population)

```

```{r}
mod_poverty_by_sex_edu_attainment <- dplyr::select(
  mod_poverty_by_sex_edu_attainment,
  NAME,
  total_population,
  below_poverty_num,
  above_poverty_num,
  poverty_percentage,
  tot_less_than_HS,
  tot_HS,
  tot_some_college,
  tot_bachelor_plus,
  HS_PLUS_percentage
)

dim(mod_poverty_by_sex_edu_attainment)


```

```{r}
file_path <- "../DATA/BUILDING_OVERVIEW_1819.xlsx"
overview_data <- read_excel(file_path, sheet = "BUILDING_OVERVIEW")

file_path <- "../DATA/BUILDING_DISCIPLINE_1819.xlsx"
discipline_data <- read_excel(file_path, sheet = "DISCIPLINE")

```

```{r}
overview_data <- dplyr::select(
  overview_data,
  "Building IRN",
  "Building Name",
  "District Name",
  "County",
  "Region",
  "Enrollment 2018-2019",
  "Attendance Rate 2018-2019",
  "Chronic Absenteeism Percent 2018-2019"
)

overview_data[,6:8] <- sapply(overview_data[,6:8],as.numeric)

discipline_data[ discipline_data == "<10" ] <- "0"
discipline_data[,8:26] <- sapply(discipline_data[,8:26],as.numeric)
discipline_data <- discipline_data[,-26]
discipline_data <- subset(discipline_data, discipline_data$`Discpline Reason Description` == "Disobedient/Disruptive Behavior")


```

```{r}
discipline_data <- dplyr::select(
  discipline_data,
  "Building IRN",
  "Students Disciplined - Expulsions",
  "Students Disciplined - Out-of-School Suspensions",
  "Students Disciplined - In-School Suspensions"
)

```

```{r}
discipline_data <- discipline_data %>% mutate(
  "total_students_discipline" = (rowSums(discipline_data[,2:4])))

joined_df <- left_join(overview_data, discipline_data, by = "Building IRN")


```

```{r}
grouped_df <- joined_df %>%
  group_by(`District Name`, County, Region) %>%
  summarise(mean_enrollment = mean(`Enrollment 2018-2019`, na.rm = TRUE),
            mean_attendence = mean(`Attendance Rate 2018-2019`, na.rm = TRUE),
            mean_chronic_absenteesim = mean(`Chronic Absenteeism Percent 2018-2019`, na.rm = TRUE),
            mean_expulsions = mean(`Students Disciplined - Expulsions`, na.rm = TRUE),
            mean_out_of_school_suspensions = mean(`Students Disciplined - Out-of-School Suspensions`, na.rm = TRUE),
            mean_in_school_suspensions = mean(`Students Disciplined - In-School Suspensions`, na.rm = TRUE),
            mean_total_students_discipline = mean(`total_students_discipline`, na.rm = TRUE))

```

```{r}
file_path <- "../DATA/model_data_3_30.csv"
model_data <- read.csv(file_path)

ggplot(model_data, aes(x=poverty_percentage, y=HS_PLUS_percentage)) + geom_point() + 
  ggtitle("Poverty % vs. Educational Attainment %") +
  xlab("Poverty %") + 
  ylab("Educational Attainment %")


ggplot(model_data, aes(x=mean_total_students_discipline, y=HS_PLUS_percentage)) + geom_point() + 
  ggtitle("Mean Student Discipline vs. Educational Attainment %") +
  xlab("Mean Student Discipline") + 
  ylab("Educational Attainment %")


ggplot(model_data, aes(x=mean_chronic_absenteeism, y=HS_PLUS_percentage)) + geom_point() + 
  ggtitle("Mean Chronic Absenteeism % vs. Educational Attainment %") +
  xlab("Mean Chronic Absenteeism %") + 
  ylab("Educational Attainment %")

ggplot(model_data, aes(x=mean_attendance, y=HS_PLUS_percentage)) + geom_point() + 
  ggtitle("Mean Attendance % vs. Educational Attainment %") +
  xlab("Mean Attendance %") + 
  ylab("Educational Attainment %")

ggplot(model_data, aes(x=mean_enrollment, y=HS_PLUS_percentage)) + geom_point() + 
  ggtitle("Mean Enrollment vs. Educational Attainment %") +
  xlab("Mean Enrollment") + 
  ylab("Educational Attainment %")


```

```{r}

file_path <- "../DATA/model_data_3_30.csv"
model_data <- read.csv(file_path)

mod_model_data <- subset(model_data, model_data$HS_PLUS_percentage > 0.65)

mod_model_data$HS_PLUS_percentage <- (((mod_model_data$HS_PLUS_percentage ^ 6) - 1) / 6)

library(gam)
library(mgcv)

```

```{r}
gam_model_1 <- gam(HS_PLUS_percentage ~ s(poverty_percentage) + s(mean_chronic_absenteeism) + s(mean_attendance) + s(mean_enrollment) + s(mean_total_students_discipline), data = mod_model_data)
summary(gam_model_1)
```

```{r}
gam.check(gam_model_1)


```

```{r}
gam_model_2 <- gam(HS_PLUS_percentage ~ s(poverty_percentage) + s(mean_chronic_absenteeism) + s(mean_attendance) + s(mean_enrollment), data = mod_model_data)
summary(gam_model_2)
```

```{r}
gam.check(gam_model_2)

```

```{r}

gam_model_3 <- gam(HS_PLUS_percentage ~ s(poverty_percentage) + s(mean_chronic_absenteeism) + s(mean_enrollment) + s(mean_total_students_discipline), data = mod_model_data)
summary(gam_model_3)
```

```{r}
gam.check(gam_model_3)


```

```{r}
anova(gam_model_1, gam_model_2, gam_model_3, test = "F")

```

```{r}
plot(gam_model_3, se=TRUE, col="blue")

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```
s

```{r}

```

