---
title: "Week 10 Markdown"
author: "Dylan Denner"
date: "3/30/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r, echo=FALSE, message=FALSE}
setwd("C:/Users/dylan/Documents/R/MATH5530/Project/MATH5530/SCRIPTS/")

# Libraries needed for analysis

library(dplyr)
library(tidycensus)
library(tidyverse)
library(tidyr)
library(readxl)
library(readr)
library(gridExtra)
library(ggpubr)
library(MASS)
library(car)
library(lmtest)

file_path <- "../DATA/model_data_3_30.csv"
model_data <- read.csv(file_path)

# Removing Outliers

mod_model_data <- subset(model_data, model_data$HS_PLUS_percentage > 0.65)
require(gridExtra)


```


```{r}
# Simple Linear Regression Models

POVERTY_lm <- lm(HS_PLUS_percentage ~ poverty_percentage, data = mod_model_data)
DISCIPLINE_lm <- lm(HS_PLUS_percentage ~ mean_total_students_discipline, data = mod_model_data)
CHRONIC_lm <- lm(HS_PLUS_percentage ~ mean_chronic_absenteeism, data = mod_model_data)
ATTENDANCE_lm <- lm(HS_PLUS_percentage ~ mean_attendance, data = mod_model_data)
ENROLLMENT_lm <- lm(HS_PLUS_percentage ~ mean_enrollment, data = mod_model_data)

```

Shapiro-Wilk Normality Test for Poverty %

```{r}
POVERTY_sresid <- studres(POVERTY_lm)
shapiro.test(POVERTY_sresid)

```

Shapiro-Wilk Normality Test for Mean Student Discipline
```{r}
DISCIPLINE_sresid <- studres(DISCIPLINE_lm)
shapiro.test(DISCIPLINE_sresid)

```


Shapiro-Wilk Normality Test for Mean Chronic Absenteeism %
```{r}
CHRONIC_sresid <- studres(CHRONIC_lm)
shapiro.test(CHRONIC_sresid)

```


Shapiro-Wilk Normality Test for Mean Attendance %
```{r}
ATTENDANCE_sresid <- studres(ATTENDANCE_lm)
shapiro.test(ATTENDANCE_sresid)

```

Shapiro-Wilk Normality Test for Mean Enrollment

```{r}
ENROLLMENT_sresid <- studres(ENROLLMENT_lm)
shapiro.test(ENROLLMENT_sresid)
```


Score Test for Non-Constant Error Variance: Poverty %
```{r}
#heterodastic
ncvTest(POVERTY_lm)

```

Score Test for Non-Constant Error Variance: Mean Student Discipline

```{r}
#homoscedastic
ncvTest(DISCIPLINE_lm)
```

Score Test for Non-Constant Error Variance: Mean Chronic Absenteeism %

```{r}
#heteroscedastic
ncvTest(CHRONIC_lm)
```

Score Test for Non-Constant Error Variance: Mean Attendance %

```{r}
#homoscedastic
ncvTest(ATTENDANCE_lm)
```

Score Test for Non-Constant Error Variance: Mean Enrollment

```{r}
#heteroscedastic
ncvTest(ENROLLMENT_lm)
```


BOXCOX Transformations

```{r}
library(MASS)
boxcox(ENROLLMENT_lm, lambda = seq(-0.25, 10, by = 0.05), plotit = TRUE)
plot1 <- plot(fitted(ENROLLMENT_lm), resid(ENROLLMENT_lm))
ENROLLMENT_lm2 <- lm((((HS_PLUS_percentage ^ 6) - 1) / 6) ~ mean_enrollment, data = mod_model_data)
plot2 <- plot(fitted(ENROLLMENT_lm2), resid(ENROLLMENT_lm2))
ENROLLMENT_sresid2 <- studres(ENROLLMENT_lm2)
shapiro.test(ENROLLMENT_sresid2)

```


```{r}
#Better P-value for normality, but still significantly Different from Normal
POVERTY_lm <- lm(HS_PLUS_percentage ~ poverty_percentage, data = mod_model_data)
boxcox(POVERTY_lm, lambda = seq(-0.25, 10, by = 0.05), plotit = TRUE)
plot1 <- plot(fitted(POVERTY_lm), resid(POVERTY_lm))
POVERTY_lm2 <- lm((((HS_PLUS_percentage ^ 6) - 1) / 6) ~ poverty_percentage, data = mod_model_data)
plot2 <- plot(fitted(POVERTY_lm2), resid(POVERTY_lm2))
POVERTY_sresid2 <- studres(POVERTY_lm2)
shapiro.test(POVERTY_sresid2)

```


```{r}
#Better P-value for normality, but still significantly Different from Normal
DISCIPLINE_lm <- lm(HS_PLUS_percentage ~ mean_total_students_discipline, data = mod_model_data)
boxcox(DISCIPLINE_lm, lambda = seq(-0.25, 10, by = 0.05), plotit = TRUE)
plot1 <- plot(fitted(DISCIPLINE_lm), resid(DISCIPLINE_lm))
DISCIPLINE_lm2 <- lm((((HS_PLUS_percentage ^ 6) - 1) / 6) ~ mean_total_students_discipline, data = mod_model_data)
plot2 <- plot(fitted(DISCIPLINE_lm2), resid(DISCIPLINE_lm2))
DISCIPLINE_sresid2 <- studres(DISCIPLINE_lm2)
shapiro.test(DISCIPLINE_sresid2)


```


```{r}
#Better P-value for normality, but still significantly Different from Normal
CHRONIC_lm <- lm(HS_PLUS_percentage ~ mean_chronic_absenteeism, data = mod_model_data)
boxcox(CHRONIC_lm, lambda = seq(-0.25, 10, by = 0.05), plotit = TRUE)
plot1 <- plot(fitted(CHRONIC_lm), resid(CHRONIC_lm))
CHRONIC_lm2 <- lm((((HS_PLUS_percentage ^ 6) - 1) / 6) ~ mean_chronic_absenteeism, data = mod_model_data)
plot2 <- plot(fitted(DISCIPLINE_lm2), resid(DISCIPLINE_lm2))
CHRONIC_sresid2 <- studres(CHRONIC_lm2)
shapiro.test(DISCIPLINE_sresid2)

```


```{r}
#Better P-value for normality, but still significantly Different from Normal
ATTENDANCE_lm <- lm(HS_PLUS_percentage ~ mean_attendance, data = mod_model_data)
boxcox(ATTENDANCE_lm, lambda = seq(-0.25, 10, by = 0.05), plotit = TRUE)
plot1 <- plot(fitted(ATTENDANCE_lm), resid(ATTENDANCE_lm))
ATTENDANCE_lm2 <- lm((((HS_PLUS_percentage ^ 6) - 1) / 6) ~ mean_attendance, data = mod_model_data)
plot2 <- plot(fitted(ATTENDANCE_lm2), resid(ATTENDANCE_lm2))
ATTENDANCE_sresid2 <- studres(ATTENDANCE_lm2)
shapiro.test(ATTENDANCE_sresid2)

```


```{r}


```



```{r}


```
